Abstract Data Type Inference

### 2015-02-27 intro.tex
Section titles.

  \item Identification of algebraic properties allowing finite
  characterizations of infinite ADT violations sets (§\ref{sec:embedding}).

  \item An under-approximating algorithm for the ADT inference problem
  (§\ref{sec:computing}).

>>>>

  \item Identification of algebraic properties allowing finite
  characterizations of infinite ADT violations sets (§\ref{sec:algebra}).

  \item An under-approximating algorithm for the ADT inference problem
  (§\ref{sec:algorithm}).
